%-------------------------------------------------------------------
\section{Numerical Examples} \label{sec:ch5:examples}

In this section, we will use five numerical examples to demonstrate the efficacy of the proposed \apgp.
The first four examples have known solutions that can be used to compute the optimal trajectories and objective function value to high precision.
Therefore, we can directly compare the different solution methods based on their deviation from the known solution.
The errors are reported as local maximum/minimum values (i.e.,~as a forward-looking moving maximum/minimum) in order to discuss the converge behavior independent of fortuitous meshes (e.g.,~the nodes points happen to be exactly at the time value where a path constraint should change activity).
In addition to comparing the absolute error, we will look at the time to create the \qp{} with the \apgp{} and the total \qp{} time (creation plus solver time).
Other performance metrics include local and global error, robustness to initial guess\footnote{The chosen solver does not require an initial guess.}, and problem size or memory needed \cite{Williams2005a, Wang2009a}.
Please see Refs.~\cite{Williams2005a, Wang2009a, Faedo2017a} for numerical comparisons between some of the \dt{} methods.
It remains future work to perform these additional comparisons.

% new paragraph
All tests were performed on a personal computer with an i7-6800K at 3.8 GHz (up to 12 threads available), 32 GB DDR4 3200 MHz RAM, \textsc{Windows} 10 64-bit, and \textsc{Matlab} 2017a.
The \qp{} solver used was the standard solver \textsc{quadprog} in \textsc{Matlab} using the \xvar{interior-point-convex} algorithm \cite{matlab-quadprog}.
All tolerances were set to $10\epsilon$, where $\epsilon$ is the machine precision number, in order to obtain the best solution possible for a particular \qp.
The complete set of codes from the \apgp{} and examples are available at Ref.~\cite{github-dt-qp-project}.

\input{../ch5/ch5_ex1}

\input{../ch5/ch5_ex2}

\input{../ch5/ch5_ex3}

\input{../ch5/ch5_ex4}

\input{../ch5/ch5_ex5}