\mychapter{\label{sec:app4:codes}Summary of Available Code\label{app:D}}

Here we summarize the available code developed as a part of this dissertation. All code is primarily written in the \textsc{Matlab} language.

\begin{enumerate}[label=$\bullet$, widest=$\bullet$, nosep]

\item \textsc{(pm architectures project)} Ref.\cite{github-pm-architectures-project} contains the code for Chapter~\ref{ch:2} and Appendix~\ref{app:A}. It generates the set of unique useful graphs with a perfect matching-based approach.
Ref.~\cite{github-perfect-matchings-of-a-complete-graph} is used in Ref.~\cite{github-pm-architectures-project} and contains a recursive algorithm for the $(n-1)!!$ perfect matchings of \glsname{K} and incomplete listings for large $n$.

\item \textsc{(co-design examples repository}) Ref.~\cite{github-co-design-examples-repository} contains the code for the examples in Chapters~\ref{ch:3}, \ref{ch:4}, and \ref{ch:7} including the \glsname[noindex]{SASA} case study. 

\item \textsc{(dt qp project)} Ref.~\cite{github-dt-qp-project} contains the code for Chapter~\ref{ch:5}, the automated problem generation for linear-quadratic dynamic optimization using direct transcription and quadratic programming. Refs.~\cite{github-optimal-control-direct-method-examples, github-basic-multiple-interval-pseudospectral} are useful teaching aids for direct methods of optimal control.

\item \textsc{(pm circuits)} Ref.~\cite{github-pm-circuits} contains the code for Chapter~\ref{ch:6}, the passive analog circuits case study including the automated model generator for creating the transfer function given the graph and automated optimization problem generation for the sizing task. 

\item \textsc{(pm suspensions)} Ref.~\cite{github-pm-suspensions} contains the code for Chapter~\ref{ch:8} including the automated model generator for creating the linearized state-space system given the graph and automated optimization problem generation utilizing Ref.~\cite{github-dt-qp-project}.

\end{enumerate}