\section{Overview}

In Chapter~\ref{ch:2}, a tree search algorithm was developed to generate a set of colored graphs covering the graph structure space defined by $(\gls{C},\gls{R},\gls{P})$ and various additional network structure constraints.
This algorithm is shown in Alg.~\ref{alg:app1:tree} with some minor changes to the variable names and the feasible edge improvement directly included.
In this appendix, a number of enhancements are proposed to either more efficiently cover the same graph structure space or allow additional network structure constraints to be defined.

\input{../app1/algorithms/alg-tree}

Each one of the enhancements will be discussed in the following format. First, the theory behind the enhancement will be presented with a focus on showing the desired graph structure space is still covered. 
Second, the implementation of the enhancement will be discussed with pseudocode. 
Finally, some examples are provided comparing the original algorithm to the enhancement. Both visualizations or other aides and computational tests are provided\footnote{A tests were performed on a personal computer with an i7-6800K at 3.8 GHz (up to 12 threads available), 32 GB DDR4 3200 MHz RAM, \textsc{windows} 10 64-bit, and \textsc{Matlab} 2017a.}.
\textit{\glsname{En}} is an abbreviation for enhancements included, \textit{\glsname{Orig}} is an abbreviation for original algorithm (see Alg.~\ref{alg:app1:tree}), and \textit{12T} is an abbreviation for 12 threads.

% new paragraph
There are six enhancements proposed in this report: replicate ordering, avoiding loops, avoiding multi-edges, avoiding line-connectivity constraints, checking for saturated subgraphs, and enumerating subcatalogs. The final section discusses the effect of the enhancements on the case studies in Chapter~\ref{ch:2}.