% new paragraph
First and foremost, it has been my honor to have been advised by Professor James T. Allison for the past six years.
His enthusiasm and guidance have provided me with continued inspiration throughout my graduate studies.
A fortuitous opportunity as an undergraduate grader was the start of a great relationship that defined my path and launched my successes.
I would also like to thank my dissertation committee for their time and valuable feedback.

% new paragraph
Most importantly, my wife, Ashley, has provided unwavering support over the past decade.
She has always been right by my side through many years of schooling, offering encouragement and the \textit{occasional} copyediting.
I also want to thank all my family and friends for their support throughout this exciting and laborious journey.

% new paragraph
I have also had the opportunity to work with many brilliant collaborators including Prof. Soon-Jo Chung, Jack Aldrich and Oscar Alvarez-Salazar from JPL, and Traci Spencer and Emily Horn from John Deere.
There are many Engineering System Design Lab (ESDL) members that have contributed in numerous ways to my success as a graduate student including: Jeff Arena, Madhav Arora, Andrew Blanco, Christian Chilan, Anand Deshmukh, Tinghao Guo, Yong Hoon Lee, Shangting Li, Danny Lohan, Jason McDonald, Marlon Mitchell, Yashwanth Nakka, Albert Patterson, Satya Peddada, Lakshmi Rao, Vedant, and many others.
I am grateful to have worked with you and I cherish our time together.

% new paragraph
Some elements of this dissertation were produced as the result of collaborative efforts.
Tinghao contributed to parts in Chapter 2 on architecture theory and the supporting code.  
Yong Hoon provided assistance in both the development of Chapter 5 on linear-quadratic dynamic optimization using direct transcription and the supporting code.
The case study in Chapter 7 was a collaborative effort among a number of coauthors with Christian as the primary lead and Yashwanth developing the beam theory model.

% new paragraph
Finally, I would like to acknowledge support from Deere \& Company, the Jet Propulsion Laboratory (JPL), the NSF center for Power Optimization of Electro-Thermal Systems (POETS), the Department of Industrial and Enterprise Systems Engineering, and the Mavis Future Faculty Fellow program.